---
title: "Programs"
author: 
  1:
    name: "Lars Vilhuber"
date: "`r Sys.Date()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Program directory
This directory contains all programs necessary to run the cleaning, analysis, etc. They can be run separately, or in a single run. 

## Setup
Most parameters are set in the `config.R`:
```{r setup_config}
source(file.path(rprojroot::find_rstudio_root_file(),"pathconfig.R"),echo=TRUE)
source(file.path(programs,"config.R"), echo=TRUE)
```

Note that the path `interwrk` is transitory, and is only kept during processing. It will be empty in the replication archive.




## Download and unpack the O&ast;NET data

 - Input data: O&ast;NET 
 - Output data: path `acquired'
 
```{r download_onet,eval=FALSE,cache=TRUE}
source(file.path(programs,"01_download_onet.R"),echo=TRUE)
```

## Mapping job titles to SOC
```{r subselect_onet,eval=FALSE,cache=TRUE}
source(file.path(programs,"02_subselect_onet.R"),echo=TRUE)
```
